Local simple connectedness of boundaries of hyperbolic groups

### 2020-04-23 paper.tex
Corrected some minor mistakes

\todo{Maybe rephrase?}
Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
condition $\S_M$ implies the local simple connectedness of $\boundary G$. We
begin by using $\S_M$ to construct a sequence of maps $(i^n_\infty)$ from the
2-skeleton of $K_n$ to $\boundary G$. These maps can be thought of as
approximate sections of $p^\infty_n$, in the following sense. For each $n$, let
$r_n\from K_n \to \Skel_2 K_n$ be a (not necessarily continuous) map sending
points to nearby points in the 2-skeleton. Then $i^n_\infty\composed r_n
\composed p^\infty_n$ converges uniformly to the identity map $\boundary G \to
\boundary G$ as $n$ tends to $\infty$. By controlling the diameter of the image
under $i^n_\infty$ of a simplex in $K_n$ we are able to prove that $\boundary
G$ is locally simply connected.

@@

\todo{Doesn't quite make sense.}
\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that the distance from $i^m_\infty \composed 
  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
  $Ca^{-m}$ for each $m \geq n_0$.
\end{lemma}

\begin{proof}
  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
  \boundary G$,
  \begin{equation*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{equation*} 
  for each $n\geq m\geq n_0$.

  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
  that
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
            - 2\delta' \\
          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
          &\geq m - C'
  \end{align*}
  for some constant $C'$.

  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
  from which the claim follows.
\end{proof}

>>>>

Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
condition $\S_M$ implies the local simple connectedness of $\boundary G$. We
begin by using $\S_M$ to construct a sequence of maps $(i^n_\infty)$ from the
2-skeleton of $K_n$ to $\boundary G$. These maps can be thought of as
approximate sections of $p^\infty_n$, in the following sense. For each $n$, let
$r_n\from K_n \to \Skel_2 K_n$ be a (not necessarily continuous) map sending
points to nearby points in the 2-skeleton. Then $i^n_\infty\composed r_n
\composed p^\infty_n$ converges uniformly to the identity map $\boundary G \to
\boundary G$ as $n$ tends to $\infty$. By controlling the diameter of the image
under $i^n_\infty$ of a simplex in $K_n$ we are able to prove that $\boundary
G$ is locally simply connected.

@@

\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that for any $m \geq n_0$, any point $\xi \in
  \boundary G$, and point $x \in \Skel_2 K_n$ contained in a simplex
  of $K_n$ containing $p^\infty_n(\xi)$, the visual distance from $\xi$ to
  $i^\infty_n(x)$ is at most $Ca^{-m}$.
\end{lemma}

\begin{proof}
  Let $m$, $\xi$ and $x$ be as in the statement of the lemma.
  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) =
  \xi$; then $\alpha(m)$ is a vertex of a simplex of $K_n$ containing
  $p^\infty_m(\xi)$. There is a path from $\alpha(m)$ to $x$ contained in the
  union of two 2-simplices of $K_n$, so by Lemma~\ref{cor:visualdiameter} it is
  sufficient to prove the lemma for $x = \alpha(m)$.

  Let $C$ be the constant appearing in Lemma~\ref{lem:linearproduct}.
  We have $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$, and
  by~\cite[Proposition III.H.1.22]{bridsonhaefliger99} there is a constant
  $\delta'$ depending only on $\delta$ such that for $n\geq m$,
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n(\alpha(m))}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{i^m_n(\alpha(m))}\} 
            - \delta' \\
          &\geq \min\{m, m - C\} - \delta' \\
          &=  m - C - \delta'.
  \end{align*}
  Therefore $\gromov{e}{\xi}{i^m_\infty(\alpha(m))} \geq m - C - \delta'$, 
  from which the claim follows.
\end{proof}
